Local to Global Mariculture Modelling

### 2025-08-15 06_run_atlantic_salmon_model.qmd
Small QOL improvements

targets::tar_validate()
# targets::tar_visnetwork(targets_only = T)
# targets::tar_outdated()
targets::tar_make(
  seconds_meta_append = 120,
  callr_function = NULL
  )
```

@@

targets::tar_validate()
targets::tar_outdated()
targets::tar_prune()

@@

meta <- targets::tar_meta() %>% 
  filter(grepl("farm_run", name))
meta$seconds %>% mean()/60 # average minutes per target
```

>>>>

targets::tar_validate()
# targets::tar_visnetwork(targets_only = T)
# targets::tar_outdated()
targets::tar_make(
  seconds_meta_append = 120,
  callr_function = NULL
  )
tar_prune()
```

@@

targets::tar_validate()
targets::tar_outdated()

@@

tar_prune()

# meta <- targets::tar_meta() %>% 
#   filter(grepl("farm_run", name))
# meta$seconds %>% mean()/60 # average minutes per target
```

### 2025-08-15 index.qmd
Small QOL improvements

---
title: "Local to Global Mariculture Modelling"
subtitle: "Project Documentation"
author: "Dr Tormey Reimer"
date: today
execute:
  eval: true
  echo: false
  warning: false
  message: false
  cache: true
knitr: 
  opts_chunk:
    fig.align: center
    fig.width: 8.5
format:
  html:
    code-fold: true
---

@@

prettyplot <- function() {
  theme_classic() +
    theme(
      text = element_text(family = "sans", size = 12, colour = "black"),
      legend.position = "none"
    )
}
```

@@

```{r}
#| label: fig-spatial-PLC
#| fig-height: 12
#| fig-cap: Total N inputs per unit biomass of salmon produced when farms are fed the MD feed (top), the PD feed (middle) or the NI feed (bottom).

plc1 <- find_read(comparisons_path, "PLC_uneat_excr_farm_summed")

@@

p_bigmap_robinson +
  geom_sf(
    data = N_ins, 
    aes(colour = mean_biom, geometry = geometry), 
    size = 2
  ) +
  coord_sf() +
  scale_color_viridis_c(option = "turbo", breaks = seq(0, 120, 10)) + 
  guides(col = guide_colourbar(
    title = expression("Total N inputs (kg/t salmon)"),
    direction = "horizontal", position = "bottom",
    label.position = "bottom", title.position = "top",
    title.vjust = 1, title.hjust = 0.5,
    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1.5,
    barheight = 1.5, barwidth = 20,
  )) +
  facet_grid(rows = vars(feed)) +
  prettyplot() +
  theme(strip.background = element_blank(), strip.text = element_blank(),
        axis.title = element_blank(),
        legend.position = "bottom")
```

```{r}
#| label: protein-inputs-patchwork-map

p_mercator <- p_bigmap_mercator +
  geom_sf(
    data = N_ins,
    aes(colour = mean_biom, geometry = geometry), 
    size = 2.5
  ) +
  coord_sf() +
  scale_color_viridis_c(option = "turbo", breaks = seq(0, 120, 10)) + #, limits = c(-30, 10)
  guides(col = guide_colourbar(
    title = expression("Total N inputs (kg/t salmon)"),
    direction = "horizontal", position = "bottom",
    label.position = "bottom", title.position = "top",
    title.vjust = 1, title.hjust = 0.5,
    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1.5,
    barheight = 1.5, barwidth = 20,
  )) +
  # facet_wrap(facets = vars(feed), nrow = 2, ncol = 2) +
  prettyplot() +
  theme(
    # strip.background = element_blank(), strip.text = element_blank(),
    legend.position = "bottom"
  ) +
  labs(y = "Latitude", x = "Longitude")

@@

harv_size %>% 
  mutate(weight = weight %>% set_units("g") %>% set_units("kg")) %>% 
  select(c(farm_ID, weight)) %>% 
  ggplot(aes(x = weight)) +
  geom_histogram(binwidth = 0.25, colour = "black", fill = "salmon", alpha = 0.75) +
  scale_y_continuous(limits = c(0,500)) +
  labs(y = "Frequency", x = "Harvest weight") +
  prettyplot() +
  theme(aspect.ratio = 0.75)
```

>>>>

---
title: "Local to Global Mariculture Modelling"
subtitle: "Project Documentation"
author: "Dr Tormey Reimer"
date: today
execute:
  eval: true
  echo: false
  warning: false
  message: false
  cache: true # quarto render index.qmd --cache-refresh
knitr: 
  opts_chunk:
    fig.align: center
    fig.width: 8.5
format:
  html:
    code-fold: true
---

@@

prettyplot <- function() {
  theme_classic() +
    theme(
      text = element_text(family = "serif", size = 14, colour = "black"),
      legend.position = "none",
      axis.title.y = element_text(margin = margin(r = 5)),
      axis.title.x = element_text(margin = margin(t = 5))
    )
}
```

@@

```{r}
#| label: fig-spatial-N-inputs
#| fig-height: 12
#| fig-cap: Total N inputs per unit biomass of salmon produced when farms are fed the MD feed (top), the PD feed (middle) or the NI feed (bottom).

@@

p_bigmap_robinson +
  geom_sf(
    data = N_ins, 
    aes(colour = mean_biom, geometry = geometry), 
    size = 2
  ) +
  coord_sf() +
  scale_color_viridis_c(option = "turbo", breaks = seq(0, 120, 10)) + 
  guides(col = guide_colourbar(
    title = expression("Total N inputs (kg/t salmon)"),
    direction = "horizontal", position = "bottom",
    label.position = "bottom", title.position = "top",
    title.vjust = 1, title.hjust = 0.5,
    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1,
    barheight = 1.5, barwidth = 20,
  )) +
  facet_grid(rows = vars(feed)) +
  # prettyplot() +
  theme(strip.background = element_blank(), strip.text = element_blank(),
        axis.title = element_blank(),
        legend.position = "bottom")
```

```{r}
#| label: N-inputs-patchwork-map

p_mercator <- p_bigmap_mercator +
  geom_sf(
    data = N_ins,
    aes(colour = mean_biom, geometry = geometry), 
    size = 2.5
  ) +
  coord_sf() +
  scale_color_viridis_c(option = "turbo", breaks = seq(0, 120, 10)) + #, limits = c(-30, 10)
  guides(col = guide_colourbar(
    title = expression("Total N inputs (kg/t salmon)"),
    direction = "horizontal", position = "bottom",
    label.position = "bottom", title.position = "top",
    title.vjust = 1, title.hjust = 0.5,
    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1,
    barheight = 1.5, barwidth = 20,
  )) +
  # facet_wrap(facets = vars(feed), nrow = 2, ncol = 2) +
  prettyplot() +
  theme(
    # strip.background = element_blank(), strip.text = element_blank(),
    legend.position = "bottom"
  ) +
  labs(y = "Latitude", x = "Longitude")

@@

harv_size %>% 
  mutate(weight = weight %>% set_units("g") %>% set_units("kg") %>% drop_units()) %>% 
  select(c(farm_ID, weight)) %>% 
  ggplot(aes(x = weight)) +
  geom_histogram(binwidth = 0.25, colour = "black", fill = "salmon", alpha = 0.75) +
  scale_y_continuous(limits = c(0,500)) +
  scale_x_continuous(breaks = seq(0,7,0.5)) +
  labs(y = "Frequency", x = "Harvest weight (kg)") +
  prettyplot() +
  theme(aspect.ratio = 0.75)
```
